---
title: "COD Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

#### Article ID: RPYAj
#### Pilot: Michael Henry Tessler
#### Co-Pilot: Tom Hardwicke
#### Start date: Mar 28 2017
#### End date: Jun 1 2017
#### Final verification: Tom Hardwicke
#### Date: Nov 12 2017

-------

#### Methods summary: 

The target article task is a "finger-mapping" reaction time study. In the baseline task, each finger (thumb to little finger) is in charge of pressing a unique button on the keyboard. The hand can either be in a typical "prone" position or upside-down in a "supine" position (the keyboard was fastened to the participant's hand so that the fingers pressed the same buttons). The baseline task served to measure each finger's reaction time in each hand position (prone vs. supine). This information was then used to adjust the main experimental data.

In the main experimental task, each participant performed each of four (4) blocks of trials.The 4 blocks corresponded to the 2 hand positions (prone vs. supine) crossed with 2 different mappings (thumb = 1 & little finger = 5; or thumb = 5 & little finger = 1).

------

#### Target outcomes: 

For this article we will focus on the findings reported for Experiment 1 in section 4.2.2. Reaction times. Specifically, we will attempt to reproduce all descriptive and inferential analyses reported in the text below and associated tables/figures:

> Corrected RTs more than two standard deviations from the overall mean were excluded from the analysis (3.4% of the data). A 2 × 2 repeated measures ANOVA with numbers direction (thumb-little finger, little finger-thumb) and hand posture (prone, supine) as within-subjects variables was carried out. A significant effect of numbers direction was found, F(1, 17) = 32.65, p < .001, η2p = .66, with faster RTs for the thumb-little finger mappings, i.e., mappings A and C (M = 508.5 ms, SD = 125), compared to little finger-thumb mappings, i.e., B and D (M = 563.2 ms, SD = 133.7) (see Fig. 2a). All the other effects were not significant.

> Next, we further explored differences in terms of ordinal position of the digits to be mapped (see Fig. 3 for RTs results as a function of mapping and of Arabic digits). In particular, since we were interested in investigating how numbers were classified depending on their position in the sequence, we performed a one-way ANOVA with Arabic digits as within-subjects variable (One, Two, Three, Four, Five). Results showed a main effect of Arabic digits on RTs, F(4, 68) = 26.23, p < .001, η2p = .61. Post-Hoc comparisons (Scheffè) revealed that digit One (M = 440.34 ms, SD = 81.19) was classified significantly faster than Two (M = 548.16 ms, SD = 93.36; p < .001), Three (M = 576.85 ms, SD = 79.95; p < .001), Four (M = 584.45 ms, SD = 104.2; p < .001) and Five (M = 529.27 ms, SD = 77.73; p < .01). Furthermore, digits Two (p < .01) and Five (p < .05) were classified significantly faster than Four.

We are also going to try and reproduce the outcomes of the baseline task as these values are needed to make adjustments in the main analysis:

> A 2x5 repeated measures analysis of variance (ANOVA) on the reaction times (RTs) of correct responses, with hand posture (prone, supine) and finger (thumb, index finger, middle finger, ring finger, little finger) as within-subjects variables was carried out. Results showed a main effect of finger, F(4, 68) = 14.17, p < .001, g2p = .47 (thumb: M = 430.67 ms, SD = 47.3; index finger: M = 414.3 ms, SD = 51.8; middle finger: M = 426.6 ms, SD = 55.6; ring finger: M = 448 ms, SD = 57; little finger: M = 424.5 ms, SD = 50.9). A main effect of hand posture was also found, F(1, 17) = 15.48, p < .002, g2p = .49, with faster RTs for the prone condition (prone posture: M = 414.3 ms, SD = 51; supine posture: M = 443.4 ms, SD = 51.7), while the interaction was not significant.

------

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)

# prepare an empty report object, we will update this each time we run compareValues2()
reportObject <- data.frame("Article_ID" = NA, "valuesChecked" = 0, "eyeballs" = 0, "Total_df" = 0, "Total_p" = 0, "Total_mean" = 0, "Total_sd" = 0, "Total_se" = 0, "Total_ci" = 0, "Total_bf" = 0, "Total_t" = 0, "Total_F" = 0, "Total_es" = 0, "Total_median" = 0, "Total_irr" = 0, "Total_r" = 0, "Total_z" = 0, "Total_coeff" = 0, "Total_n" = 0, "Total_x2" = 0, "Total_other" = 0, "Insufficient_Information_Errors" = 0, "Decision_Errors" = 0, "Major_Numerical_Errors" = 0, "Minor_Numerical_Errors" = 0, "Major_df" = 0, "Major_p" = 0, "Major_mean" = 0, "Major_sd" = 0, "Major_se" = 0, "Major_ci" = 0, "Major_bf" = 0, "Major_t" = 0, "Major_F" = 0, "Major_es" = 0, "Major_median" = 0, "Major_irr" = 0, "Major_r" = 0, "Major_z" = 0, "Major_coeff" = 0, "Major_n" = 0, "Major_x2" = 0, "Major_other" = 0, "affectsConclusion" = NA, "error_typo" = 0, "error_specification" = 0, "error_analysis" = 0, "error_data" = 0, "error_unidentified" = 0, "Author_Assistance" = NA, "resolved_typo" = 0, "resolved_specification" = 0, "resolved_analysis" = 0, "resolved_data" = 0, "correctionSuggested" = NA, "correctionPublished" = NA)
```

## Step 1: Load packages

Some useful packages are being loaded below.

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(CODreports) # custom report functions
library(agricolae) # for posthoc Scheffe tests
library(afex) # for anova
```

## Step 2: Load data

```{r}
df.raw <- read_tsv("data/raw-data.txt")
df.baseline <- read_tsv("data/baseline-data.txt");
df.corrected <- read_tsv("data/corrected-data.txt");
```

## Step 3: Tidy data

For baseline, data is already in tidy format. Here we make some minor adjustments to the data format:

```{r}
df.baseline <- df.baseline %>%
  rename(Posture = `Hand Posture`) %>%
  mutate(Posture = factor(Posture, levels = c("Up", "Down"), labels = c("Supine", "Prone")),
         Finger = factor(Image),
         Subject = factor(Subject)
)
```

Check we have 18 participants:
```{r}
length(unique(df.baseline$Subject))
```

Ok.

For corrected RTs, it appears that columns correspond to experimental conditions X finger number and values are in milliseconds (so 32510 is 325.10 ms)

```{r}
df.corrected <- df.corrected %>%
  select(-X22) %>% # remove empty column
  gather(condition, rt, -Subject) %>%
  separate(condition, into = c("Mapping", "Number")) %>%
  mutate(rt = rt / 100) %>%
  mutate(Mapping = factor(Mapping),
         Number = factor(Number),
         Subject = factor(Subject))
```


## Step 4: Run analysis

### Baseline task

We first try to reproduce the analysis of the baseline task as we will need this data to make adjustments for the main experimental task.

> Motor baseline task
> A preliminary analysis was carried out to check possible differences in the motor baseline task. The overall error rate was 2.6% for the prone posture and 2.3% for the supine posture. 

```{r}
baseline.errorRates <- df.baseline %>%
  group_by(Posture) %>%
  summarise(errorRate = (1 - mean(Accuracy))) %>%
  ungroup() %>%
  spread(Posture, errorRate)

## compare obtained error rates
reportObject <- compareValues2(
  reportedValue = "0.026",
  obtainedValue = baseline.errorRates$Prone,
  valueType = 'mean')

reportObject <- compareValues2(
  reportedValue = "0.023",
  obtainedValue = baseline.errorRates$Supine,
  valueType = 'mean')
```

#### Descriptive statistics

Let's now try and reproduce the outcomes reported here:

> A 2x5 repeated measures analysis of variance (ANOVA) on the reaction times (RTs) of correct responses, with hand posture (prone, supine) and finger (thumb, index finger, middle finger, ring finger, little finger) as within-subjects variables was carried out. Results showed a main effect of finger, F(4, 68) = 14.17, p < .001, g2p = .47 (thumb: M = 430.67 ms, SD = 47.3; index finger: M = 414.3 ms, SD = 51.8; middle finger: M = 426.6 ms, SD = 55.6; ring finger: M = 448 ms, SD = 57; little finger: M = 424.5 ms, SD = 50.9). A main effect of hand posture was also found, F(1, 17) = 15.48, p < .002, g2p = .49, with faster RTs for the prone condition (prone posture: M = 414.3 ms, SD = 51; supine posture: M = 443.4 ms, SD = 51.7), while the interaction was not significant.

```{r}
# create a participant level dataset
participantLevel <- df.baseline %>%
  filter(Accuracy == 1) %>% # select only correct responses
  group_by(Subject, Posture, Finger) %>%
  summarize(RT = mean(RT)) %>%
  ungroup()
```

Calculate summary statistics for Finger condition:

```{r}
sumStats <- participantLevel %>%
  group_by(Finger) %>%
  summarise(M = mean(RT), SD = sd(RT))

sumStats
```

Looks like there are a number of discrepancies here. Let's check them explicitly:

```{r}
# thumb: M = 430.67 ms, SD = 47.3
m1 <- sumStats %>% filter(Finger == "Thumb") %>% pull(M)
sd1 <- sumStats %>% filter(Finger == "Thumb") %>% pull(SD)
reportObject <- compareValues2(reportedValue = "430.67", obtainedValue = m1, valueType = 'mean')
reportObject <- compareValues2(reportedValue = "47.3", obtainedValue = sd1, valueType = 'sd')

# index finger: M = 414.3 ms, SD = 51.8
m2 <- sumStats %>% filter(Finger == "Index") %>% pull(M)
sd2 <- sumStats %>% filter(Finger == "Index") %>% pull(SD)
reportObject <- compareValues2(reportedValue = "414.3", obtainedValue = m2, valueType = 'mean')
reportObject <- compareValues2(reportedValue = "51.8", obtainedValue = sd2, valueType = 'sd')

# middle finger: M = 426.6 ms, SD = 55.6
m3 <- sumStats %>% filter(Finger == "Middle Finger") %>% pull(M)
sd3 <- sumStats %>% filter(Finger == "Middle Finger") %>% pull(SD)
reportObject <- compareValues2(reportedValue = "426.6", obtainedValue = m3, valueType = 'mean')
reportObject <- compareValues2(reportedValue = "55.6", obtainedValue = sd3, valueType = 'sd')

# ring finger: M = 448 ms, SD = 57
m4 <- sumStats %>% filter(Finger == "Ring Finger") %>% pull(M)
sd4 <- sumStats %>% filter(Finger == "Ring Finger") %>% pull(SD)
reportObject <- compareValues2(reportedValue = "448", obtainedValue = m4, valueType = 'mean')
reportObject <- compareValues2(reportedValue = "57", obtainedValue = sd4, valueType = 'sd')

# little finger: M = 424.5 ms, SD = 50.9
m5 <- sumStats %>% filter(Finger == "Little Finger") %>% pull(M)
sd5 <- sumStats %>% filter(Finger == "Little Finger") %>% pull(SD)
reportObject <- compareValues2(reportedValue = "424.5", obtainedValue = m5, valueType = 'mean')
reportObject <- compareValues2(reportedValue = "50.9", obtainedValue = sd5, valueType = 'sd')
```

There are a large number of discrepancies here and it is unclear why.

```{r}
# calculate summary statistics for posture
sumStats <- participantLevel %>%
  group_by(Posture) %>%
  summarise(M = mean(RT), SD = sd(RT))

sumStats
```

There are discrepancies here too. Let's compare the values explicitly:

```{r}
# prone posture: M = 414.3 ms, SD = 51
m6 <- sumStats %>% filter(Posture == "Prone") %>% pull(M)
sd6 <- sumStats %>% filter(Posture == "Prone") %>% pull(SD)
reportObject <- compareValues2(reportedValue = "414.3", obtainedValue = m6, valueType = 'mean')
reportObject <- compareValues2(reportedValue = "51", obtainedValue = sd6, valueType = 'sd')

# supine posture: M = 443.4 ms, SD = 51.7
m7 <- sumStats %>% filter(Posture == "Supine") %>% pull(M)
sd7 <- sumStats %>% filter(Posture == "Supine") %>% pull(SD)
reportObject <- compareValues2(reportedValue = "443.4", obtainedValue = m7, valueType = 'mean')
reportObject <- compareValues2(reportedValue = "51.7", obtainedValue = sd7, valueType = 'sd')
```

There are discrepancies with these values too.

#### Inferential statistics

Let's have a look at the anova.

> A 2x5 repeated measures analysis of variance (ANOVA) on the reaction times (RTs) of correct responses, with hand posture (prone, supine) and finger (thumb, index finger, middle finger, ring finger, little finger) as within-subjects variables was carried out. 

```{r}
# anova
aov1 <- aov(RT ~ Posture*Finger + Error(Subject/(Posture*Finger)), data=participantLevel)

# create output for SPSS to double check anova
forSPSS <- participantLevel %>%
  mutate(condition = paste(Posture, "_", Finger)) %>%
  select(Subject, condition, RT) %>%
  spread(condition, RT)
```

Let's compare the reported anova output:

> Results showed a main effect of finger, F(4, 68) = 14.17, p < .001, g2p = .47 ...A main effect of hand posture was also found, F(1, 17) = 15.48, p < .002, g2p = .49...while the interaction was not significant.

to the anova output we obtained:

```{r}
summary(aov1)
```

Many discrepancies here. Let's compare them explicitly:

```{r}
# a main effect of finger, F(4, 68) = 14.17, p < .001
reportObject <- compareValues2(reportedValue = "4", obtainedValue = 4, valueType = 'df') # df value
reportObject <- compareValues2(reportedValue = "68", obtainedValue = 68, valueType = 'df') # df value
reportObject <- compareValues2(reportedValue = "14.17", obtainedValue = 15.71, valueType = 'F') # f value
reportObject <- compareValues2(reportedValue = "eyeballMATCH", obtainedValue = 0.00000000375, valueType = 'p') # p value

# A main effect of hand posture was also found, F(1, 17) = 15.48, p < .002,
reportObject <- compareValues2(reportedValue = "1", obtainedValue = 1, valueType = 'df') # df value
reportObject <- compareValues2(reportedValue = "17", obtainedValue = 17, valueType = 'df') # df value
reportObject <- compareValues2(reportedValue = "15.48", obtainedValue = 12.72, valueType = 'F')
reportObject <- compareValues2(reportedValue = "eyeballMATCH", obtainedValue = 0.00238, valueType = 'p') # p value
```

We have encountered a large number of problems reproducing the values reported for the baseline task. We contacted the authors about this, and they attempted to reproduce the values themselves. They said that they also could not reproduce the values for the baseline task. They were not sure why these problems occurred. However, a data file containing the reaction times (RTs) for the main analysis corrected for baseline was also shared with the article, and the authors say that they are confident these values are correct. Note that the authors cannot reproduce them using the baseline values, but say that the baseline values must be wrong and the RTs for the main analysis were corrected using the correct baseline values. We will therefore attempt to reproduce the main analysis using the corrected RTs data file rather than re-calculating these values from scratch using the baseline values as we had initially intended.

### Main analysis

#### Pre-processing

> Corrected RTs more than two standard deviations from the overall mean were excluded from the analysis (3.4% of the data). (Section 4.2.2)

```{r}
globalMean <- mean(df.corrected$rt)
globalSD <- sd(df.corrected$rt)

df.corrected <- df.corrected %>% # identify any outliers
  mutate(outlier = ( (rt > globalMean + 2*globalSD) || 
                       (rt < globalMean - 2*globalSD) ))

df.corrected.filtered <- df.corrected %>% filter(!outlier)

reportedOutlierRate = 0.034

mean(df.corrected$outlier)
```

It seems like the excluded RTs are already excluded from the published data set.

The experimental data is just coded for Mapping (i.e., "condition": A, B, C, D). According to Section 4.1.3 paragraph 2 (with help from Figure 2b), conditions A & B are Posture = "Down" (or "prone") and C & D are Posture = "Up" (or supine).

In addition, we will add 'direction', thumb-little and little-thumb as shown in Figure 2b.


Thumb-little was used in conditions A and C, and little-thumb in B and D.

```{r}
conditionPostures <- data.frame(
  Mapping = c("A", "B", "C", "D"),
  Posture = c("Prone", "Prone", "Supine", "Supine"),
  Direction = c("thumb-little", "little-thumb", "thumb-little", "little-thumb")
)


df.corrected <- left_join(df.corrected, conditionPostures)
```

#### Descriptive statistics

We will now try and reproduce the following target outcomes:

> A 2 × 2 repeated measures ANOVA with numbers direction (thumb-little finger, little finger-thumb) and hand posture (prone, supine) as within-subjects variables was carried out. A significant effect of numbers direction was found, F(1, 17) = 32.65, p < .001, η2p = .66, with faster RTs for the thumb-little finger mappings, i.e., mappings A and C (M = 508.5 ms, SD = 125), compared to little finger-thumb mappings, i.e., B and D (M = 563.2 ms, SD = 133.7) (see Fig. 2a). All the other effects were not significant.

We'll only look at the descriptive statistics now (inferentials are checked below).

```{r}
df.corrected.summary <- df.corrected %>%
  group_by(Direction) %>%
  summarize( m = mean(rt), 
             sd = sd(rt))

df.corrected.summary
```

Explictly compare:

```{r}
reportObject <- compareValues2(
  reportedValue = "508.5",
  obtainedValue = filter(df.corrected.summary, Direction == "thumb-little")$m,
  valueType = 'mean'
)

reportObject <- compareValues2(
  reportedValue = "125",
  obtainedValue = filter(df.corrected.summary, Direction == "thumb-little")$sd,
  valueType = 'sd'
)

reportObject <- compareValues2(
  reportedValue =  "563.2",
  obtainedValue = filter(df.corrected.summary, Direction == "little-thumb")$m,
  valueType = 'mean'
)

reportObject <- compareValues2(
  reportedValue = "133.7",
  obtainedValue = filter(df.corrected.summary, Direction == "little-thumb")$sd,
  valueType = 'sd'
)
```

We will now try and reproduce the following target outcomes:

> Next, we further explored differences in terms of ordinal position of the digits to be mapped (see Fig. 3 for RTs results as a function of mapping and of Arabic digits). In particular, since we were interested in investigating how numbers were classified depending on their position in the sequence, we performed a one-way ANOVA with Arabic digits as within-subjects variable (One, Two, Three, Four, Five). Results showed a main effect of Arabic digits on RTs, F(4, 68) = 26.23, p < .001, η2p = .61. Post-Hoc comparisons (Scheffè) revealed that digit One (M = 440.34 ms, SD = 81.19) was classified significantly faster than Two (M = 548.16 ms, SD = 93.36; p < .001), Three (M = 576.85 ms, SD = 79.95; p < .001), Four (M = 584.45 ms, SD = 104.2; p < .001) and Five (M = 529.27 ms, SD = 77.73; p < .01). Furthermore, digits Two (p < .01) and Five (p < .05) were classified significantly faster than Four.

We'll only look at the descriptive statistics now (inferentials are checked below).

```{r}
df.corrected.digits.summary <- df.corrected %>%
  group_by(Subject, Number) %>% # first summarise at subject level
  summarize(subRT = mean(rt)) %>%
  group_by(Number) %>%
  summarize( m = mean(subRT), 
             sd = sd(subRT))

df.corrected.digits.summary
```

Compare explictly:

```{r}
reportObject <- compareValues2(
  reportedValue = "440.34",
  obtainedValue = filter(df.corrected.digits.summary, Number == 1)$m,
  valueType = 'mean'
)

reportObject <- compareValues2(
  reportedValue = "81.19",
  obtainedValue = filter(df.corrected.digits.summary, Number == 1)$sd,
  valueType = 'sd'
)

reportObject <- compareValues2(
  reportedValue = "548.16",
  obtainedValue = filter(df.corrected.digits.summary, Number == 2)$m,
  valueType = 'mean'
)

reportObject <- compareValues2(
  reportedValue = "93.36",
  obtainedValue = filter(df.corrected.digits.summary, Number == 2)$sd,
  valueType = 'sd'
)

reportObject <- compareValues2(
  reportedValue = "576.85",
  obtainedValue = filter(df.corrected.digits.summary, Number == 3)$m,
  valueType = 'mean'
)

reportObject <- compareValues2(
  reportedValue = "79.95",
  obtainedValue = filter(df.corrected.digits.summary, Number == 3)$sd,
  valueType = 'sd'
)

reportObject <- compareValues2(
  reportedValue = "584.45",
  obtainedValue = filter(df.corrected.digits.summary, Number == 4)$m,
  valueType = 'mean'
)

reportObject <- compareValues2(
  reportedValue = "104.2",
  obtainedValue = filter(df.corrected.digits.summary, Number == 4)$sd,
  valueType = 'sd'
)

reportObject <- compareValues2(
  reportedValue = "529.27",
  obtainedValue = filter(df.corrected.digits.summary, Number == 5)$m,
  valueType = 'mean'
)

reportObject <- compareValues2(
  reportedValue = "77.73",
  obtainedValue = filter(df.corrected.digits.summary, Number ==5)$sd,
  valueType = 'sd'
)
```

All looks ok.

#### Inferential statistics

We will now try and reproduce the following target outcomes:

> A 2 × 2 repeated measures ANOVA with numbers direction (thumb-little finger, little finger-thumb) and hand posture (prone, supine) as within-subjects variables was carried out. A significant effect of numbers direction was found, F(1, 17) = 32.65, p < .001, η2p = .66, with faster RTs for the thumb-little finger mappings, i.e., mappings A and C (M = 508.5 ms, SD = 125), compared to little finger-thumb mappings, i.e., B and D (M = 563.2 ms, SD = 133.7) (see Fig. 2a). All the other effects were not significant.

We'll only look at the inferential statistics now (descritives are checked above).

```{r}
rs.aov <- aov_ez(data = df.corrected, id = "Subject", dv = "rt", within = c("Posture", "Direction"), anova_table = list(correction = "none", es = "pes"), type = 'III')

reportObject <- compareValues2( # compare df value
  reportedValue = "1",
  obtainedValue = rs.aov$anova_table$`num Df`[[2]],
  valueType = 'df'
)
reportObject <- compareValues2( # compare df value
  reportedValue = "17",
  obtainedValue = rs.aov$anova_table$`den Df`[[2]],
  valueType = 'df'
)

reportObject <- compareValues2( # compare F value
  reportedValue = "32.65",
  obtainedValue = rs.aov$anova_table$`F`[[2]],
  valueType = 'F'
)

reportObject <- compareValues2( # compare p value
  reportedValue = "eyeballMATCH",
  obtainedValue = rs.aov$anova_table$`Pr(>F)`[[2]],
  valueType = 'p'
)

reportObject <- compareValues2( # compare p value
  reportedValue = ".66",
  obtainedValue = rs.aov$anova_table$`pes`[[2]],
  valueType = 'es'
)
```

All looks fine.

We will now try and reproduce the following target outcomes:

> Next, we further explored differences in terms of ordinal position of the digits to be mapped (see Fig. 3 for RTs results as a function of mapping and of Arabic digits). In particular, since we were interested in investigating how numbers were classified depending on their position in the sequence, we performed a one-way ANOVA with Arabic digits as within-subjects variable (One, Two, Three, Four, Five). Results showed a main effect of Arabic digits on RTs, F(4, 68) = 26.23, p < .001, η2p = .61.

```{r}
rs.aov.digits <- aov_ez(data = df.corrected, dv = "rt", id = "Subject", within = "Number", anova_table = list(correction = "none", es = "pes"), type = 'III')

reportObject <- compareValues2( # compare df values
  reportedValue = "4",
  obtainedValue = rs.aov.digits$anova_table$`num Df`,
  valueType = 'df'
)

reportObject <- compareValues2( # compare df values
  reportedValue = "68",
  obtainedValue = rs.aov.digits$anova_table$`den Df`,
  valueType = 'df'
)
 
reportObject <- compareValues2( # compare F values
  reportedValue = "26.23",
  obtainedValue =  rs.aov.digits$anova_table$`F`,
  valueType = 'F'
)

reportObject <- compareValues2( # compare F values
  reportedValue = ".61",
  obtainedValue =  rs.aov.digits$anova_table$`pes`,
  valueType = 'es'
)

reportObject <- compareValues2( # compare F values
  reportedValue = "eyeballMATCH",
  obtainedValue =  rs.aov.digits$anova_table$`Pr(>F)`,
  valueType = 'p'
)
```

Looks fine.

## Step 5: Conclusion

We encountered a large number of problems reproducing the values reported for the baseline task. We contacted the authors about this, and they attempted to reproduce the values themselves. They said that they also could not reproduce the values for the baseline task. They were not sure why these problems occurred. However, a data file containing the reaction times (RTs) for the main analysis corrected for baseline was also shared with the article, and the authors say that they are confident these values are correct. Note that the authors cannot reproduce them using the baseline values, but say that the baseline values must be wrong and the RTs for the main analysis were corrected using the correct baseline values. 

We then attempted to reproduce the main analysis using the corrected RTs data file rather than re-calculating these values from scratch using the baseline values as we had initially intended. The main analysis reproduced fine.

```{r}
reportObject$Article_ID <- "RPYAj"
reportObject$affectsConclusion <- "no"
reportObject$error_typo <- 0
reportObject$error_specification <- 0
reportObject$error_analysis <- 0
reportObject$error_data <- 0
reportObject$error_unidentified <- 1
reportObject$Author_Assistance <- T
reportObject$resolved_typo <- 0
reportObject$resolved_specification <- 0
reportObject$resolved_analysis <- 0
reportObject$resolved_data <- 0
reportObject$correctionSuggested <- "no"
reportObject$correctionPublished <- F

# decide on final outcome
if(reportObject$Decision_Errors > 0 | reportObject$Major_Numerical_Errors > 0 | reportObject$Insufficient_Information_Errors > 0){
  reportObject$finalOutcome <- "Failure"
  if(reportObject$Author_Assistance == T){
    reportObject$finalOutcome <- "Failure despite author assistance"
  }
}else{
  reportObject$finalOutcome <- "Success"
  if(reportObject$Author_Assistance == T){
    reportObject$finalOutcome <- "Success with author assistance"
  }
}

# save the report object
filename <- paste0("reportObject_", reportObject$Article_ID,".csv")
write_csv(reportObject, filename)
```

## Report Object

```{r, echo = FALSE}
# display report object in chunks
kable(reportObject[2:10], align = 'l')
kable(reportObject[11:20], align = 'l')
kable(reportObject[21:25], align = 'l')
kable(reportObject[26:30], align = 'l')
kable(reportObject[31:35], align = 'l')
kable(reportObject[36:40], align = 'l')
kable(reportObject[41:45], align = 'l')
kable(reportObject[46:51], align = 'l')
kable(reportObject[52:57], align = 'l')
```

## Session information

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
