---
title: "COD Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

#### Article ID: RPYAj
#### Pilot: Michael Henry Tessler
#### Start date: 03/28/17
#### End date: 04/07/17 

-------

#### Methods summary: 

The target article task is a "finger-mapping" reaction time study. 

In the baseline task, each finger (thumb to little finger) is in charge of pressing a unique button the keyboard.
The hand can either be in a typical "prone" position or upside-down in a "supine" position (the keyboard was fastened to the participant's hand so that the fingers pressed the same buttons). 
The baseline task serves to measure each finger's reaction time in each hand position (prone vs. supine).
This information is then used to adjust the main experimental data.

In the main experimental task, each participant performs each of four (4) blocks of trials. 
The 4 blocks correspond to the 2 hand positions (prone vs. supine) crossed with 2 different mappings (thumb = 1 & little finger = 5; or thumb = 5 & little finger = 1).

------

#### Target outcomes: 

For this article you should focus on the findings reported for Experiment 1 in section 4.2.2. Reaction times. Specifically, you should attempt to reproduce all descriptive and inferential analyses reported in the text below and associated tables/figures:

> Corrected RTs more than two standard deviations from the overall mean were excluded from the analysis (3.4% of the data). A 2 × 2 repeated measures ANOVA with numbers direction (thumb-little finger, little finger-thumb) and hand posture (prone, supine) as within-subjects variables was carried out. A significant effect of numbers direction was found, F(1, 17) = 32.65, p < .001, η2p = .66, with faster RTs for the thumb-little finger mappings, i.e., mappings A and C (M = 508.5 ms, SD = 125), compared to little finger-thumb mappings, i.e., B and D (M = 563.2 ms, SD = 133.7) (see Fig. 2a). All the other effects were not significant.

> Next, we further explored differences in terms of ordinal position of the digits to be mapped (see Fig. 3 for RTs results as a function of mapping and of Arabic digits). In particular, since we were interested in investigating how numbers were classified depending on their position in the sequence, we performed a one-way ANOVA with Arabic digits as within-subjects variable (One, Two, Three, Four, Five). Results showed a main effect of Arabic digits on RTs, F(4, 68) = 26.23, p < .001, η2p = .61. Post-Hoc comparisons (Scheffè) revealed that digit One (M = 440.34 ms, SD = 81.19) was classified significantly faster than Two (M = 548.16 ms, SD = 93.36; p < .001), Three (M = 576.85 ms, SD = 79.95; p < .001), Four (M = 584.45 ms, SD = 104.2; p < .001) and Five (M = 529.27 ms, SD = 77.73; p < .01). Furthermore, digits Two (p < .01) and Five (p < .05) were classified significantly faster than Four.

**Note**
Make sure to use the original article for additional context and information about any necessary pre-processing steps. Also check for additional supplementary materials that may provide supporting documentation for analysis procedures.


------

[The chunk below sets up some formatting options for the R Markdown document]

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

## Step 1: Load packages

[Some useful packages are being loaded below. You can add any additional ones you might need too.]

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(CODreports) # custom report functions
library(agricolae) # for posthoc Scheffe tests
```

## Step 2: Load data

```{r}
df.raw <- read_tsv("data/raw-data.txt")
df.baseline <- read_tsv("data/baseline-data.txt");
```



## Step 3: Tidy data

```{r}
df.baseline <- df.baseline %>%
  rename(Posture = `Hand Posture`) %>%
  mutate(Posture = factor(Posture, levels = c("Up", "Down"), labels = c("Supine", "Prone")),
         Image = factor(Image)
)
```


Data is already in tidy format.

## Step 4: Run analysis

### Baseline task

> Motor baseline task
> A preliminary analysis was carried out to check possible differ- ences in the motor baseline task. The overall error rate was 2.6% for the prone posture and 2.3% for the supine posture. A 2x5 repeated measures analysis of variance (ANOVA) on the reaction times (RTs) of correct responses, with hand posture (prone, supine) and finger (thumb, index finger, middle finger, ring finger, little finger) as within-subjects variables was carried out. Results showed a main effect of finger, F(4, 68) = 14.17, p < .001, g2p = .47 (thumb: M = 430.67 ms, SD = 47.3; index finger: M = 414.3 ms, SD = 51.8; middle finger: M = 426.6 ms, SD = 55.6; ring finger: M = 448 ms, SD = 57; little finger: M = 424.5 ms, SD = 50.9). A main effect of hand posture was also found, F(1, 17) = 15.48, p < .002, g2p = .49, with faster RTs for the prone condition (prone posture: M = 414.3 ms, SD = 51; supine posture: M = 443.4 ms, SD = 51.7), while the interaction was not significant.


#### Descriptive statistics

```{r baseline.descriptives}

baseline.decriptives <- list(
  "Thumb" = list(m = 430.67, sd = 47.3),
  "Index" = list(m = 414.3, sd = 51.8),
  "Middle Finger" = list(m = 426.6, sd = 55.6),
  "Ring Finger" = list(m = 448, sd = 57),
  "Little Finger" = list(m = 424.5, sd = 50.9),
  "Prone" = list(m = 414.3, sd = 51),
  "Supine" = list(m = 443.4, sd = 51.7),
  "Error" = list(Prone = 0.026, Supine = 0.023)
)

baseline.errorRates <- df.baseline %>%
  group_by(Posture) %>%
  summarise(errorRate = (1 - mean(Accuracy))) %>%
  ungroup() %>%
  spread(Posture, errorRate)

## compare obtained error rates
compareValues(
  reportedValue = baseline.decriptives$Error$Prone,
  obtainedValue = round(baseline.errorRates$Prone, 3)
)

compareValues(
  reportedValue = baseline.decriptives$Error$Supine,
  obtainedValue = round(baseline.errorRates$Supine, 3)
)


df.baseline.summary <- df.baseline %>%
  filter(Accuracy == 1) %>%
  group_by(Subject, Posture, Image) %>%
  summarize(meanRT = mean(RT)) %>%
  ungroup() %>%
  group_by(Image) %>%
  summarize(M = mean(meanRT),
            SD = sd(meanRT))

## compare obtained means and sd for each finger

compareValues(
  reportedValue = baseline.decriptives$Thumb$m, 
  obtainedValue = filter(df.baseline.summary, Image == "Thumb")$M
  )

compareValues(
  reportedValue = baseline.decriptives$Thumb$sd, 
  obtainedValue = filter(df.baseline.summary, Image == "Thumb")$SD
  )

compareValues(
  reportedValue = baseline.decriptives$Index$m, 
  obtainedValue = filter(df.baseline.summary, Image == "Index")$M
  )

compareValues(
  reportedValue = baseline.decriptives$Index$sd, 
  obtainedValue = filter(df.baseline.summary, Image == "Index")$SD
  )

compareValues(
  reportedValue = baseline.decriptives$`Middle Finger`$m, 
  obtainedValue = filter(df.baseline.summary, Image == "Middle Finger")$M
  )

compareValues(
  reportedValue = baseline.decriptives$`Middle Finger`$sd, 
  obtainedValue = filter(df.baseline.summary, Image == "Middle Finger")$SD
  )

compareValues(
  reportedValue = baseline.decriptives$`Ring Finger`$m, 
  obtainedValue = filter(df.baseline.summary, Image == "Ring Finger")$M
  )

compareValues(
  reportedValue = baseline.decriptives$`Ring Finger`$sd, 
  obtainedValue = filter(df.baseline.summary, Image == "Ring Finger")$SD
  )


compareValues(
  reportedValue = baseline.decriptives$`Little Finger`$m, 
  obtainedValue = filter(df.baseline.summary, Image == "Little Finger")$M
  )

compareValues(
  reportedValue = baseline.decriptives$`Little Finger`$sd, 
  obtainedValue = filter(df.baseline.summary, Image == "Little Finger")$SD
  )

df.baseline.summary.position <- df.baseline %>%
  filter(Accuracy == 1) %>%
  group_by(Subject, Posture, Image) %>%
  summarize(meanRT = mean(RT)) %>%
  ungroup() %>%
  group_by(Posture) %>%
  summarize(M = mean(meanRT),
            SD = sd(meanRT))

## compare obtained means and sd for each hand position

compareValues(
  reportedValue = baseline.decriptives$Prone$m, 
  obtainedValue = filter(df.baseline.summary.position, Posture == "Prone")$M
  )

compareValues(
  reportedValue = baseline.decriptives$Prone$sd, 
  obtainedValue = filter(df.baseline.summary.position, Posture == "Prone")$SD
  )

compareValues(
  reportedValue = baseline.decriptives$Supine$m, 
  obtainedValue = filter(df.baseline.summary.position, Posture == "Supine")$M
  )

compareValues(
  reportedValue = baseline.decriptives$Supine$sd, 
  obtainedValue = filter(df.baseline.summary.position, Posture == "Supine")$SD
  )
```

#### Inferential statistics

```{r}
df.baseline.subject <- df.baseline %>%
  filter(Accuracy == 1) %>%
  group_by(Subject, Posture, Image) %>%
  summarize(meanRT = mean(RT))


baseline.inferentials <- list(
  Posture = list (f = 15.48, p = 0.002),
  Finger = list(f = 14.17, p = 0.001)
)


# ggplot(df.baseline.summary, aes(x = meanRT, fill = Posture))+
#   #geom_histogram(position = position_dodge())
#   geom_density(alpha = 0.5)


rs.aov.baseline <-aov(meanRT ~ 
                        Posture * Image + Error(Subject / (Posture * Image)), 
  data = df.baseline.subject)

rs.aov.baseline.summary <- summary(rs.aov.baseline)

compareValues(
  reportedValue = baseline.inferentials$Finger$f,
  obtainedValue = rs.aov.baseline.summary$`Error: Within`[[1]]["Image","F value"]
)

compareValues(
  reportedValue = baseline.inferentials$Finger$p,
  obtainedValue = rs.aov.baseline.summary$`Error: Within`[[1]]["Image","Pr(>F)"],
  isP = T
)


compareValues(
  reportedValue = baseline.inferentials$Posture$f,
  obtainedValue = rs.aov.baseline.summary$`Error: Within`[[1]]["Posture      ","F value"]
)

compareValues(
  reportedValue = baseline.inferentials$Posture$p,
  obtainedValue = rs.aov.baseline.summary$`Error: Within`[[1]]["Posture      ","Pr(>F)"],
  isP = T
)

```



### Pre-processing of main task data

The following preprocessing was applied to the baseline data to then clean the raw data. (p.44, s.4.1.5)

> To avoid any possible confounding motor effects, we first calculated for each participant the average RT of each finger in each posture. 

```{r baseline.averages}
df.baseline.ave <- df.baseline %>%
  filter(Accuracy == 1) %>% # analysis only performed on correct responses
  group_by(Subject, Posture, Image, CorrectResponse) %>%
  summarize(aveRT = mean(RT)) 

# ggplot(df.baseline.ave, aes( x = aveRT, fill = Posture))+
#   geom_histogram(position = position_dodge())
```

> Then, the RT of the fastest finger was subtracted from the RT of each other finger, obtaining an index of each finger relative speed (i.e., finger D). 

It's not clear to me if this is within Posture or not (i.e., fastest finger when hand is down? or just fastest finger overall?; I will assume the latter.)

```{r finger.delta}
finger.d <- df.baseline.ave %>%
  ungroup() %>%
  group_by(Subject) %>%
  mutate(fastest = min(aveRT)) %>%
  ungroup() %>%
  mutate(fingerD = aveRT - fastest) %>%
  select(-aveRT, -fastest)
```


> The finger D was then subtracted from the average RT of each finger in each experimental mapping, resulting in a corrected finger RT. 

The baseline data is coded for posture (Supine vs. Prone) x image (i.e., finger).
The experimental (raw) data is just coded for Mapping (i.e., "condition": A, B, C, D).
According to Section 4.1.3 paragraph 2 (with help from Figure 2b), conditions A & B are Posture = "Down" (or "prone") and C & D are Posture = "Up" (or supine).

In addition, we will later need the 1->5 vs. 5->1 mapping as a separate variable.
1->5 was used in conditions A and D, and 5->1 in B and C.

The variable CorrectResponse is shared between both data sets and is the same variable as Image (i.e., finger).

```{r corrected.responses}
conditionPostures <- data.frame(
  Mapping = c("A", "B", "C", "D"),
  Posture = c("Prone", "Prone", "Supine", "Supine"),
  Direction = c("1->5", "5->1", "5->1", "1->5")
)

df.expt.averages <- df.raw %>%
  filter(Accuracy == 1) %>%
  group_by(Subject, Mapping, CorrectResponse) %>%
  summarize(aveRT = mean(RT))

df.corrected <- left_join(df.expt.averages, left_join(finger.d, conditionPostures)) %>%
  mutate(correctedRT = aveRT - fingerD)
```


> A further correction was applied to avoid confounding effects of hand posture. Due to the faster performance in the prone posture, for each participant the average RT of each finger in the prone posture was subtracted from its average RT in the supine posture (i.e., posture D). 

I assume we are still talking about the baseline data set.

```{r posture.delta}
posture.d <- df.baseline.ave %>%
  ungroup() %>%
  spread(Posture, aveRT) %>%
  mutate(postureD = Supine - Prone)

#qplot(data = posture.d, x = postureD, geom = 'histogram')
# sanity check: should be mostly greater than 0
```


> The posture D was then subtracted from the average RT of each finger in each experimental mapping of the supine posture, resulting in a corrected supine finger RT. Only RTs of correct responses were analyzed in the experimental sessions and we separately performed an analysis of errors.

I assume we are applying this to the already corrected RTs.
We are subtracting `postureD` from the (already fingerD-corrected) RTs for the supine (Up) posture only.
My approach here is to take the `postureD` colun in `posture.d` and label those as "Up" for posture. 
I'll then bind rows corresponding to the "Down" posture with `postureD = 0`, so no correction will be applied to the "down" or prone posture.

```{r}
df.corrected2 <- left_join(
  df.corrected,
  bind_rows(
    posture.d %>%
      select(Subject, Image, CorrectResponse, postureD) %>%
      mutate(Posture = "Supine"),
    posture.d %>%
      select(Subject, Image, CorrectResponse) %>%
      mutate(Posture = "Prone", postureD = 0)
  )
) %>% 
  mutate(postureCorrectedRT = correctedRT - postureD)
```

### Main experimental results

#### Descriptive statistics

> Corrected RTs more than two standard deviations from the overall mean were excluded from the analysis (3.4% of the data). (Section 4.2.2)

```{r}
globalMean <- mean(df.corrected2$postureCorrectedRT)
globalSD <- sd(df.corrected2$postureCorrectedRT)

df.corrected2 <- df.corrected2 %>%
  mutate(outlier = ( (postureCorrectedRT > globalMean + 2*globalSD) || 
                       (postureCorrectedRT < globalMean - 2*globalSD) ))

df.corrected2.filtered <- df.corrected2 %>% filter(!outlier)

reportedOutlierRate = 0.034

compareValues(reportedValue = reportedOutlierRate, obtainedValue = mean(df.corrected2$outlier))

```

> A 2 × 2 repeated measures ANOVA with numbers direction (thumb-little finger, little finger-thumb) and hand posture (prone, supine) as within-subjects variables was carried out. A significant effect of numbers direction was found, F(1, 17) = 32.65, p < .001, η2p = .66, with faster RTs for the thumb-little finger mappings, i.e., mappings A and C (M = 508.5 ms, SD = 125), compared to little finger-thumb mappings, i.e., B and D (M = 563.2 ms, SD = 133.7) (see Fig. 2a). All the other effects were not significant.



```{r}
reported.descriptives <- list(
  ac = list( m = 508.5, sd = 125),
  bd = list( m = 563.2, sd = 133.7)
)

df.corrected2.filtered.summaries <- df.corrected2.filtered %>%
  group_by(Direction) %>%
  summarize( m = mean(postureCorrectedRT), 
             sd = sqrt(var(postureD)))

directionsConditions <- list(
 "ac" =  "1->5","bd"="5->1"
)

compareValues(
  reportedValue = reported.descriptives$ac$m,
  obtainedValue = filter(df.corrected2.filtered.summaries, Direction == directionsConditions[["ac"]])$m
)

compareValues(
  reportedValue = reported.descriptives$ac$sd,
  obtainedValue = filter(df.corrected2.filtered.summaries, Direction == directionsConditions[["ac"]])$sd
)

compareValues(
  reportedValue = reported.descriptives$bd$m,
  obtainedValue = filter(df.corrected2.filtered.summaries, Direction == directionsConditions[["bd"]])$m
)

compareValues(
  reportedValue = reported.descriptives$bd$sd,
  obtainedValue = filter(df.corrected2.filtered.summaries, Direction == directionsConditions[["bd"]])$sd
)
```



#### Inferential statistics

> A 2 × 2 repeated measures ANOVA with numbers direction (thumb-little finger, little finger-thumb) and hand posture (prone, supine) as within-subjects variables was carried out. A significant effect of numbers direction was found, F(1, 17) = 32.65, p < .001, η2p = .66, with faster RTs for the thumb-little finger mappings, i.e., mappings A and C (M = 508.5 ms, SD = 125), compared to little finger-thumb mappings, i.e., B and D (M = 563.2 ms, SD = 133.7) (see Fig. 2a). All the other effects were not significant.


```{r}
reported.inferentials  <- list(
  f = 32.65, p = 0.001
)


rs.aov <- with(df.corrected2.filtered, 
     aov(postureCorrectedRT ~ Posture * Direction + Error(Subject / (Posture * Direction))))

rs.aov.summary <- summary(rs.aov)

compareValues(
  reportedValue = reported.inferentials$f,
  obtainedValue = rs.aov.summary$`Error: Within`[[1]]["Direction","F value"]
)

compareValues(
  reportedValue = reported.inferentials$p,
  obtainedValue = rs.aov.summary$`Error: Within`[[1]]["Direction","Pr(>F)"],
  isP = T
)
```

> Next, we further explored differences in terms of ordinal position of the digits to be mapped (see Fig. 3 for RTs results as a function of mapping and of Arabic digits). In particular, since we were interested in investigating how numbers were classified depending on their position in the sequence, we performed a one-way ANOVA with Arabic digits as within-subjects variable (One, Two, Three, Four, Five). Results showed a main effect of Arabic digits on RTs, F(4, 68) = 26.23, p < .001, η2p = .61. 

Arabic digits are a function of both hand position and direction. 

```{r}
arabicDigitsAC = list(
   "Thumb" = 1,
   "Index" = 2,
   "Middle Finger" = 3,
   "Ring Finger" = 4,
   "Little Finger" = 5
)
arabicDigitsBD = list(
   "Thumb" = 5,
   "Index" = 4,
   "Middle Finger" = 3,
   "Ring Finger" = 2,
   "Little Finger" = 1
)

df.corrected2.filtered.digits <- bind_rows(
  df.corrected2.filtered %>% 
    filter(Mapping %in% c("A", "C")) %>%
    rowwise() %>%
    mutate(digit = arabicDigitsAC[[as.character(Image)]]),
  df.corrected2.filtered %>% 
    filter(Mapping %in% c("B", "D")) %>%
    rowwise() %>%
    mutate(digit = arabicDigitsBD[[as.character(Image)]])
)
      
```


```{r}
reported.inferentials.position  <- list(
  f = 26.23, p = 0.001
)


rs.aov.digits <- with(df.corrected2.filtered.digits, 
     aov(postureCorrectedRT ~ digit))

rs.aov.digits.summary <- summary(rs.aov.digits)


compareValues(
  reportedValue = reported.inferentials.position$f,
  obtainedValue = rs.aov.digits.summary[[1]]["digit","F value"]
)

compareValues(
  reportedValue = reported.inferentials.position$p,
  obtainedValue = rs.aov.digits.summary[[1]]["digit","Pr(>F)"],
  isP = T
)
```


> Post-Hoc comparisons (Scheffè) revealed that digit One (M = 440.34 ms, SD = 81.19) was classified significantly faster than Two (M = 548.16 ms, SD = 93.36; p < .001), Three (M = 576.85 ms, SD = 79.95; p < .001), Four (M = 584.45 ms, SD = 104.2; p < .001) and Five (M = 529.27 ms, SD = 77.73; p < .01). Furthermore, digits Two (p < .01) and Five (p < .05) were classified significantly faster than Four.

```{r}
posthoc.descriptives = list(
  "1" = list(m = 440.34, sd = 81.19),
  "2" = list(m = 548.16, sd = 93.36),
  "3" = list(m = 576.85, sd = 79.95),
  "4" = list(m = 584.45, sd = 104.2),
  "5" = list(m = 529.27, sd = 77.73)
)

df.corrected2.filtered.digits.summary <- df.corrected2.filtered.digits %>%
  ungroup() %>%
  group_by(digit) %>%
  summarize( m = mean(postureCorrectedRT),
             sd = sqrt(var(postureCorrectedRT)))

## compare obtained means and sd for each digit

compareValues(
  reportedValue = posthoc.descriptives[["1"]]$m, 
  obtainedValue = filter(df.corrected2.filtered.digits.summary, digit == 1)$m
  )

compareValues(
  reportedValue = posthoc.descriptives[["1"]]$sd, 
  obtainedValue = filter(df.corrected2.filtered.digits.summary, digit == 1)$sd
  )

compareValues(
  reportedValue = posthoc.descriptives[["2"]]$m, 
  obtainedValue = filter(df.corrected2.filtered.digits.summary, digit == 2)$m
  )

compareValues(
  reportedValue = posthoc.descriptives[["2"]]$sd, 
  obtainedValue = filter(df.corrected2.filtered.digits.summary, digit == 2)$sd
  )

compareValues(
  reportedValue = posthoc.descriptives[["3"]]$m, 
  obtainedValue = filter(df.corrected2.filtered.digits.summary, digit == 3)$m
  )

compareValues(
  reportedValue = posthoc.descriptives[["3"]]$sd, 
  obtainedValue = filter(df.corrected2.filtered.digits.summary, digit == 3)$sd
  )

compareValues(
  reportedValue = posthoc.descriptives[["4"]]$m, 
  obtainedValue = filter(df.corrected2.filtered.digits.summary, digit == 4)$m
  )

compareValues(
  reportedValue = posthoc.descriptives[["4"]]$sd, 
  obtainedValue = filter(df.corrected2.filtered.digits.summary, digit == 4)$sd
  )


compareValues(
  reportedValue = posthoc.descriptives[["5"]]$m, 
  obtainedValue = filter(df.corrected2.filtered.digits.summary, digit == 5)$m
  )

compareValues(
  reportedValue = posthoc.descriptives[["5"]]$sd, 
  obtainedValue = filter(df.corrected2.filtered.digits.summary, digit == 5)$sd
  )


```
```{r}
posthoc.tests <- scheffe.test(rs.aov.digits, "digit", group=TRUE, main="Adjusted reaction times \nDealt with different digits")
posthoc.tests
```

I'm not sure how to get p-values out of this, but seeing how the descriptive statistics are off, the inferentials will be off too.


## Step 5: Conclusion

This was a rather tricky analysis, which failed to reproduce all but the first descriptive statistics (the error rate). 
The likely causes could be:

1. Misinterpretation of the data file: This is more of an issue for the experimental data `df.raw` and not the baseline data `df.baseline`, because the baseline data are inherenetly simpler.
2. Incorrect implementation of a within-subjects 2x2 ANOVA: These are the first ANOVAs I've done, and I'm not 100% confident in my method.
3. Incorrect implementation of the preprocessing pipeline: There was a complicated preprocessing algorithm, that I may have misintereprted.


```{r}
codReport(Report_Type = 'pilot',
          Article_ID = 'RPYAj', 
          Insufficient_Information_Errors = 0,
          Decision_Errors = 4, 
          Major_Numerical_Errors = 24, 
          Minor_Numerical_Errors = 14)
```

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
