---
title: "COD Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

#### Article ID: RPYAj
#### Pilot: Michael Henry Tessler
#### Co-pilot: Tom Hardwicke  
#### Start date: 03/28/17
#### End date: [Insert end date - use US format]   

-------

After contacting the authors, it was suggested that we try to reproduce the analysis not from the raw data but from the "corrected RT" data. 


#### Methods summary: 

The target article task is a "finger-mapping" reaction time study. 

In the baseline task, each finger (thumb to little finger) is in charge of pressing a unique button the keyboard.
The hand can either be in a typical "prone" position or upside-down in a "supine" position (the keyboard was fastened to the participant's hand so that the fingers pressed the same buttons). 
The baseline task serves to measure each finger's reaction time in each hand position (prone vs. supine).
This information is then used to adjust the main experimental data.

In the main experimental task, each participant performs each of four (4) blocks of trials. 
The 4 blocks correspond to the 2 hand positions (prone vs. supine) crossed with 2 different mappings (thumb = 1 & little finger = 5; or thumb = 5 & little finger = 1).

------

#### Target outcomes: 

For this article you should focus on the findings reported for Experiment 1 in section 4.2.2. Reaction times. Specifically, you should attempt to reproduce all descriptive and inferential analyses reported in the text below and associated tables/figures:

> Corrected RTs more than two standard deviations from the overall mean were excluded from the analysis (3.4% of the data). A 2 × 2 repeated measures ANOVA with numbers direction (thumb-little finger, little finger-thumb) and hand posture (prone, supine) as within-subjects variables was carried out. A significant effect of numbers direction was found, F(1, 17) = 32.65, p < .001, η2p = .66, with faster RTs for the thumb-little finger mappings, i.e., mappings A and C (M = 508.5 ms, SD = 125), compared to little finger-thumb mappings, i.e., B and D (M = 563.2 ms, SD = 133.7) (see Fig. 2a). All the other effects were not significant.

> Next, we further explored differences in terms of ordinal position of the digits to be mapped (see Fig. 3 for RTs results as a function of mapping and of Arabic digits). In particular, since we were interested in investigating how numbers were classified depending on their position in the sequence, we performed a one-way ANOVA with Arabic digits as within-subjects variable (One, Two, Three, Four, Five). Results showed a main effect of Arabic digits on RTs, F(4, 68) = 26.23, p < .001, η2p = .61. Post-Hoc comparisons (Scheffè) revealed that digit One (M = 440.34 ms, SD = 81.19) was classified significantly faster than Two (M = 548.16 ms, SD = 93.36; p < .001), Three (M = 576.85 ms, SD = 79.95; p < .001), Four (M = 584.45 ms, SD = 104.2; p < .001) and Five (M = 529.27 ms, SD = 77.73; p < .01). Furthermore, digits Two (p < .01) and Five (p < .05) were classified significantly faster than Four.

**Note**
Make sure to use the original article for additional context and information about any necessary pre-processing steps. Also check for additional supplementary materials that may provide supporting documentation for analysis procedures.


------


```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

## Step 1: Load packages

[Some useful packages are being loaded below. You can add any additional ones you might need too.]

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(CODreports) # custom report functions
library(agricolae) # for posthoc Scheffe tests
```

## Step 2: Load data

```{r}
df.corrected <- read_tsv("data/corrected-data.txt")
```

I believe rows correspond to experimental conditions X finger number 
Values are in milliseconds / 100 (so 32510 is 325.10 ms)


## Step 3: Tidy data

```{r}
df.tidy <- df.corrected %>%
  select(-X22) %>% # remove empty column
  gather(condition, rt, -Subject) %>%
  separate(condition, into = c("Mapping", "Number")) %>%
  mutate(rt = rt / 100)
```


## Step 4: Run analysis

### Baseline task

> Motor baseline task
> A preliminary analysis was carried out to check possible differ- ences in the motor baseline task. The overall error rate was 2.6% for the prone posture and 2.3% for the supine posture. A 2x5 repeated measures analysis of variance (ANOVA) on the reaction times (RTs) of correct responses, with hand posture (prone, supine) and finger (thumb, index finger, middle finger, ring finger, little finger) as within-subjects variables was carried out. Results showed a main effect of finger, F(4, 68) = 14.17, p < .001, g2p = .47 (thumb: M = 430.67 ms, SD = 47.3; index finger: M = 414.3 ms, SD = 51.8; middle finger: M = 426.6 ms, SD = 55.6; ring finger: M = 448 ms, SD = 57; little finger: M = 424.5 ms, SD = 50.9). A main effect of hand posture was also found, F(1, 17) = 15.48, p < .002, g2p = .49, with faster RTs for the prone condition (prone posture: M = 414.3 ms, SD = 51; supine posture: M = 443.4 ms, SD = 51.7), while the interaction was not significant.


### Pre-processing of main task data


The experimental data is just coded for Mapping (i.e., "condition": A, B, C, D).
According to Section 4.1.3 paragraph 2 (with help from Figure 2b), conditions A & B are Posture = "Down" (or "prone") and C & D are Posture = "Up" (or supine).

In addition, we will later need the 1->5 vs. 5->1 mapping as a separate variable.
1->5 was used in conditions A and D, and 5->1 in B and C.


### Main experimental results

#### Descriptive statistics

> Corrected RTs more than two standard deviations from the overall mean were excluded from the analysis (3.4% of the data). (Section 4.2.2)

```{r}
globalMean <- mean(df.tidy$rt)
globalSD <- sd(df.tidy$rt)

df.tidy <- df.tidy %>%
  mutate(outlier = ( (rt > globalMean + 2*globalSD) || 
                       (rt < globalMean - 2*globalSD) ))

df.tidy.filtered <- df.tidy %>% filter(!outlier)

reportedOutlierRate = 0.034

compareValues(reportedValue = reportedOutlierRate, 
              obtainedValue = mean(df.tidy$outlier))

```

It seems like the excluded RTs are already excluded from the published data set.


> A 2 × 2 repeated measures ANOVA with numbers direction (thumb-little finger, little finger-thumb) and hand posture (prone, supine) as within-subjects variables was carried out. A significant effect of numbers direction was found, F(1, 17) = 32.65, p < .001, η2p = .66, with faster RTs for the thumb-little finger mappings, i.e., mappings A and C (M = 508.5 ms, SD = 125), compared to little finger-thumb mappings, i.e., B and D (M = 563.2 ms, SD = 133.7) (see Fig. 2a). All the other effects were not significant.



```{r}
conditionPostures <- data.frame(
  Mapping = c("A", "B", "C", "D"),
  Posture = c("Prone", "Prone", "Supine", "Supine"),
  Direction = c("1->5", "5->1", "5->1", "1->5")
)


df.tidy <- left_join(df.tidy, conditionPostures)

reported.descriptives <- list(
  ac = list( m = 508.5, sd = 125),
  bd = list( m = 563.2, sd = 133.7)
)

df.tidy.summaries <- df.tidy %>%
  group_by(Direction) %>%
  summarize( m = mean(rt), 
             sd = sqrt(var(rt)))

directionsConditions <- list(
 "ac" =  "1->5", "bd"="5->1"
)

compareValues(
  reportedValue = reported.descriptives$ac$m,
  obtainedValue = filter(df.tidy.summaries, Direction == directionsConditions[["ac"]])$m
)

compareValues(
  reportedValue = reported.descriptives$ac$sd,
  obtainedValue = filter(df.tidy.summaries, Direction == directionsConditions[["ac"]])$sd
)

compareValues(
  reportedValue = reported.descriptives$bd$m,
  obtainedValue = filter(df.tidy.summaries, Direction == directionsConditions[["bd"]])$m
)

compareValues(
  reportedValue = reported.descriptives$bd$sd,
  obtainedValue = filter(df.tidy.summaries, Direction == directionsConditions[["bd"]])$sd
)
```

#### Inferential statistics

> A 2 × 2 repeated measures ANOVA with numbers direction (thumb-little finger, little finger-thumb) and hand posture (prone, supine) as within-subjects variables was carried out. A significant effect of numbers direction was found, F(1, 17) = 32.65, p < .001, η2p = .66, with faster RTs for the thumb-little finger mappings, i.e., mappings A and C (M = 508.5 ms, SD = 125), compared to little finger-thumb mappings, i.e., B and D (M = 563.2 ms, SD = 133.7) (see Fig. 2a). All the other effects were not significant.


```{r}
reported.inferentials  <- list(
  f = 32.65, p = 0.001
)


rs.aov <- with(df.tidy, 
     aov(rt ~ Posture * Direction + Error(Subject / (Posture * Direction))))

rs.aov.summary <- summary(rs.aov)

compareValues(
  reportedValue = reported.inferentials$f,
  obtainedValue = rs.aov.summary$`Error: Within`[[1]]["Direction","F value"]
)

compareValues(
  reportedValue = reported.inferentials$p,
  obtainedValue = rs.aov.summary$`Error: Within`[[1]]["Direction","Pr(>F)"],
  isP = T
)
```

> Next, we further explored differences in terms of ordinal position of the digits to be mapped (see Fig. 3 for RTs results as a function of mapping and of Arabic digits). In particular, since we were interested in investigating how numbers were classified depending on their position in the sequence, we performed a one-way ANOVA with Arabic digits as within-subjects variable (One, Two, Three, Four, Five). Results showed a main effect of Arabic digits on RTs, F(4, 68) = 26.23, p < .001, η2p = .61. 

Arabic digits are a function of both hand position and direction. 

I believe the arabic digit information is already present in the corrected RT data file.

# ```{r}
# arabicDigitsAC = list(
#    "Thumb" = 1,
#    "Index" = 2,
#    "Middle Finger" = 3,
#    "Ring Finger" = 4,
#    "Little Finger" = 5
# )
# arabicDigitsBD = list(
#    "Thumb" = 5,
#    "Index" = 4,
#    "Middle Finger" = 3,
#    "Ring Finger" = 2,
#    "Little Finger" = 1
# )
# 
# df.corrected2.filtered.digits <- bind_rows(
#   df.tidy %>% 
#     filter(Mapping %in% c("A", "C")) %>%
#     rowwise() %>%
#     mutate(digit = arabicDigitsAC[[as.character(Image)]]),
#   df.tidy %>% 
#     filter(Mapping %in% c("B", "D")) %>%
#     rowwise() %>%
#     mutate(digit = arabicDigitsBD[[as.character(Image)]])
# )
#       
# ```

```{r}
reported.inferentials.position  <- list(
  f = 26.23, p = 0.001
)


rs.aov.digits <- with(df.tidy, aov(rt ~ Number))

rs.aov.digits.summary <- summary(rs.aov.digits)


compareValues(
  reportedValue = reported.inferentials.position$f,
  obtainedValue = rs.aov.digits.summary[[1]]["Number","F value"]
)

compareValues(
  reportedValue = reported.inferentials.position$p,
  obtainedValue = rs.aov.digits.summary[[1]]["Number","Pr(>F)"],
  isP = T
)
```


> Post-Hoc comparisons (Scheffè) revealed that digit One (M = 440.34 ms, SD = 81.19) was classified significantly faster than Two (M = 548.16 ms, SD = 93.36; p < .001), Three (M = 576.85 ms, SD = 79.95; p < .001), Four (M = 584.45 ms, SD = 104.2; p < .001) and Five (M = 529.27 ms, SD = 77.73; p < .01). Furthermore, digits Two (p < .01) and Five (p < .05) were classified significantly faster than Four.

```{r}
posthoc.descriptives = list(
  "1" = list(m = 440.34, sd = 81.19),
  "2" = list(m = 548.16, sd = 93.36),
  "3" = list(m = 576.85, sd = 79.95),
  "4" = list(m = 584.45, sd = 104.2),
  "5" = list(m = 529.27, sd = 77.73)
)

df.tidy.digits.summary <- df.tidy %>%
  ungroup() %>%
  group_by(Number) %>%
  summarize( m = mean(rt),
             sd = sqrt(var(rt)))

## compare obtained means and sd for each digit

compareValues(
  reportedValue = posthoc.descriptives[["1"]]$m, 
  obtainedValue = filter(df.tidy.digits.summary, Number == 1)$m
  )

compareValues(
  reportedValue = posthoc.descriptives[["1"]]$sd, 
  obtainedValue = filter(df.tidy.digits.summary, Number == 1)$sd
  )

compareValues(
  reportedValue = posthoc.descriptives[["2"]]$m, 
  obtainedValue = filter(df.tidy.digits.summary, Number == 2)$m
  )

compareValues(
  reportedValue = posthoc.descriptives[["2"]]$sd, 
  obtainedValue = filter(df.tidy.digits.summary, Number == 2)$sd
  )

compareValues(
  reportedValue = posthoc.descriptives[["3"]]$m, 
  obtainedValue = filter(df.tidy.digits.summary, Number == 3)$m
  )

compareValues(
  reportedValue = posthoc.descriptives[["3"]]$sd, 
  obtainedValue = filter(df.tidy.digits.summary, Number == 3)$sd
  )

compareValues(
  reportedValue = posthoc.descriptives[["4"]]$m, 
  obtainedValue = filter(df.tidy.digits.summary, Number == 4)$m
  )

compareValues(
  reportedValue = posthoc.descriptives[["4"]]$sd, 
  obtainedValue = filter(df.tidy.digits.summary, Number == 4)$sd
  )


compareValues(
  reportedValue = posthoc.descriptives[["5"]]$m, 
  obtainedValue = filter(df.tidy.digits.summary, Number == 5)$m
  )

compareValues(
  reportedValue = posthoc.descriptives[["5"]]$sd, 
  obtainedValue = filter(df.tidy.digits.summary, Number == 5)$sd
  )
```

```{r}
posthoc.tests <- scheffe.test(rs.aov.digits, "Number", group=TRUE, main="Adjusted reaction times \nDealt with different digits")
posthoc.tests
```

I'm not sure how to get p-values out of this, but seeing how the descriptive statistics are off, the inferentials will be off too.


## Step 5: Conclusion

I tried to analyze this data set again starting from what I presume are the already corrected RT data. 

One possible cause of my familiar is a misinterpretation of the data file. The data was recorded by "Letter_Number". The Letter is quite obviously the experimental condition (coded as A, B, C, D). The Number is a little more opaque, but I guess is the "Digit" (so the identity of the finger is not in this data set).


A second possible cause of the failure is an incorrect implementation of a within-subjects 2x2 ANOVA: These are the first ANOVAs I've done, and I'm not 100% confident in my method.


```{r}
codReport(Report_Type = 'pilot',
          Article_ID = 'RPYAj', 
          Insufficient_Information_Errors = 0,
          Decision_Errors = 1, 
          Major_Numerical_Errors = 10, 
          Minor_Numerical_Errors = 9)
```

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
